|

### 2020-09-15 paper.Rmd
google bib added year

XXX probably remove this, for now keeping it in for reference
see also discussion in https://mc-stan.org/users/documentation/case-studies/curse-dims.html on the average length of multivariate normal vector for large $p$, relation to "concentration of measures".

>>>>

<!-- XXX probably remove this, for now keeping it in for reference
see also discussion in https://mc-stan.org/users/documentation/case-studies/curse-dims.html on the average length of multivariate normal vector for large $p$, relation to "concentration of measures".-->
